### 2014-01-23 rscripts/manuscript.Rnw
tweaks

One syntactical aside for the code the below sections: the Scala collections (like \texttt{Set}) define methods for adding and removing elements in terms of the natural mathematical operators (\texttt{+} and \texttt{-}) and for similar operations with groups of elements (\texttt{++} and \texttt{--}).  Similarly, the names for message senders (\texttt{sender}), changing context (\texttt{context become ...}), et cetera are all quite clear.  Given the informative, mixed-natural-and-mathematical-like syntax, we use actual code snippets instead of pseudo-code to illustrate.

>>>>

One syntactical aside for the code the below sections: the Scala collections (like \texttt{Set}) define methods for adding and removing elements in terms of the natural mathematical operators (\texttt{+}, \texttt{-}) and for similar operations with groups of elements (\texttt{++}, \texttt{--}).  Similarly, the names for message senders (\texttt{sender}), changing context (\texttt{context become ...}), et cetera are all quite clear.  Given the informative, mixed-natural-and-mathematical-like syntax, we prefer actual code snippets to pseudo-code to illustrate simulation steps.
